---
title: "Costs of Exercise versus Exercise-Plus interventions on falls"
author: "RSF"
date: "2022-08-17"
output: 
  html_document:
    toc: true
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1) Data set-up and management

Load Packages
```{r}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(readxl, plyr, robumeta,metafor, clubSandwich, ggplot2, psych, naniar)
```

Import and Prep Data for Meta-Analysis
```{r}
setwd("~/Desktop/Manuscripts/Ongoing Projects/Cost Analysis of Unimodal vs. Multimodal Exercise Interventions for Fall Prevention")#Directory where you put the spreadsheet
meta_data <- read_excel("META FINAL FINAL.xlsx")

spaceless <- function(x) {colnames(x) <- gsub(" ", "_", colnames(x));x}
meta_data_spaceless <- spaceless(meta_data)

data1<-meta_data_spaceless %>% replace_with_na_all(condition = ~.x == "NR")
data2<-subset(data1, Exclude=="No")

library(dplyr)
data3<-rename(data2, "Sample_size"="Total_number_of_participants","Intervention_Type"="Intervention_Type_(EX,_EX-PluS)",
              "Intervention_Mode"="Intervention_Mode_(AT,_RT,_Multimodal)", "Intervention_Frequency"="Intervention_Frequency_(days/week)",
              "Intervention_Duration"="Intervention_Duration_(weeks)", "Economic_Perspective"="Economic_Perspective_(Healthcare,_Societal,_Personal)",
              "Incremental_Costs"="Incremental_costs_in_2021_USD","Incremental_Costs_SE"="Incremental_costs_standard_error_in_2021_USD",
              "Estimated_Incremental_Costs_SE"="Estimated_Standard_Error_(Using_similar_study_with_similar_SE)",
              "Incremental_QOLYs_SE"="Incremental_QoLYs_standard_error_in_2021_USD","Estimated_QOLYs_SE"="Estimated_SE_for_QoLYs_(Using_study_with_similar_SE)",
              "IRR_of_Falls"="Mean_Difference_in_IRR_of_Falls", "IRR_of_Falls_SE"="IRR_Standard_Error_of_estimate",
              "Estimated_IRR_of_Falls_SE"="Estimated_SE_of_IRR", "INT_N"="Treatment_group_sample_size", "CON_N"="Control_group_sample_size")


data4<-data3 %>% 
  mutate(
    Incremental_Costs_SE_Final = case_when(
      !is.na(Incremental_Costs_SE) ~ Incremental_Costs_SE,
      !is.na(Estimated_Incremental_Costs_SE) ~ Estimated_Incremental_Costs_SE
      ),
    Incremental_QOLYs_SE_Final = case_when(
      !is.na(Incremental_QOLYs_SE) ~ Incremental_QOLYs_SE,
      !is.na(Estimated_QOLYs_SE) ~ Estimated_QOLYs_SE
    ),
    IRR_of_Falls_SE_Final = case_when(
      !is.na(IRR_of_Falls_SE) ~ IRR_of_Falls_SE,
      !is.na(Estimated_IRR_of_Falls_SE) ~ Estimated_IRR_of_Falls_SE
    ),
    Incremental_Costs_SMD = Incremental_Costs/Incremental_Costs_SE_Final,
    Incremental_QOLYs_SMD = Incremental_QoLYs/Incremental_QOLYs_SE_Final,
    IRR_of_Falls_SMD = log(IRR_of_Falls),
    J = 1 - (3/(4*INT_N + CON_N - 2) - 1),
    Incremental_Costs_Variance = (Sample_size*Incremental_Costs_SE_Final),
    Incremental_QOLYs_Variance = (Sample_size*Incremental_QOLYs_SE_Final),
    Incremental_Costs_SMD_var = ((INT_N + CON_N)/(INT_N*CON_N)) + ((Incremental_Costs_SMD^2)/(2*(INT_N+CON_N))),
    Incremental_QOLYs_SMD_var = ((INT_N + CON_N)/(INT_N*CON_N)) + ((Incremental_QOLYs_SMD^2)/(2*(INT_N+CON_N))),
    IRR_of_Falls_SMD_var = ((INT_N + CON_N)/(INT_N*CON_N)) + ((IRR_of_Falls_SMD^2)/(2*(INT_N+CON_N))),
    Incremental_Costs_g = Incremental_Costs_SMD * J,
    Incremental_Costs_g_var = J^2 * Incremental_Costs_SMD_var,
    Incremental_Costs_g_se = sqrt(Incremental_Costs_g_var/Sample_size),
    Incremental_QOLYs_g = Incremental_QOLYs_SMD * J,
    Incremental_QOLYs_g_var = J^2 * Incremental_QOLYs_SMD_var,
    Incremental_QOLYs_g_se = sqrt(Incremental_QOLYs_g_var/Sample_size),
    IRR_of_Falls_g = IRR_of_Falls_SMD * J,
    IRR_of_Falls_g_var = J^2 * IRR_of_Falls_SMD_var,
    IRR_of_Falls_g_se = sqrt(IRR_of_Falls_g_var/Sample_size),
    Incremental_Costs_UL95CI = Incremental_Costs + 1.96*Incremental_QOLYs_SE_Final,
    Incremental_Costs_LL95CI = Incremental_Costs - 1.96*Incremental_QOLYs_SE_Final,
    Incremental_QOLYs_UL95CI = Incremental_QoLYs + 1.96*Incremental_QOLYs_SE_Final,
    Incremental_QOLYs_LL95CI = Incremental_QoLYs - 1.96*Incremental_QOLYs_SE_Final,
    IRR_Falls_SMD_UL95CI = IRR_of_Falls_g + 1.96*IRR_of_Falls_g_se,
    IRR_Falls_SMD_LL95CI = IRR_of_Falls_g - 1.96*IRR_of_Falls_g_se
  )
```

# 2) Descriptive Analyses for Meta

Number of effect sizes for incremental cost
```{r}
nrow(data4[!is.na(data4$Incremental_Costs_g),])
```

Number of studies with effect sizes for incremental costs
```{r}
Incremental_costs<-subset(data4, !is.na(Incremental_Costs_g))
Incremental_costs %>%
  count(Study_ID)
```

Number of studies with effect sizes for incremental costs by intervention type
```{r}
Incremental_costs %>%
  count(Study_ID, Intervention_Type)
```

Number of participants included in effect sizes for incremental costs
```{r}
sum(Incremental_costs$Sample_size)
```

Number of effect sizes for incremental QALYs
```{r}
nrow(data4[!is.na(data4$Incremental_QOLYs_g),])
```

Number of studies with effect sizes for incremental QALYs
```{r}
Incremental_QOLYs<-subset(data4, !is.na(Incremental_QOLYs_g))
Incremental_QOLYs %>%
  count(Study_ID)
```

Number of studies with effect sizes for incremental QALYs by intervention type
```{r}
Incremental_QOLYs %>%
  count(Study_ID, Intervention_Type)
```

Number of participants included in effect sizes for incremental QALYs
```{r}
sum(Incremental_QOLYs$Sample_size)
```

Number of effect sizes for IRR of Falls
```{r}
nrow(data4[!is.na(data4$IRR_of_Falls_g),])
```

Number of studies with effect sizes for IRR of Falls
```{r}
IRR_Falls<-subset(data4, !is.na(IRR_of_Falls_g))
IRR_Falls %>%
  count(Study_ID)
```

Number of studies with effect sizes for IRR of Falls by intervention type
```{r}
IRR_Falls %>%
  count(Study_ID, Intervention_Type)
```

Number of participants included in effect sizes for IRR of Falls
```{r}
sum(IRR_Falls$Sample_size)
```

Sample size total
```{r}
table(data4$Study_ID,data4$Sample_size)
123+155+217+233+240+301+323+340+364+381+409+450+830+1090+6420+9803      
```

# 3) Main Effect Sizes for Incremental Costs, QALYs, and IRR of Falls

Incremental Costs (Unstandardized estimates)
```{r}
incremental_costs.unstandardized<-robu(Incremental_Costs~1, var=Incremental_Costs_Variance, studynum=Study_ID, Incremental_costs)
print(incremental_costs.unstandardized)
sensitivity(incremental_costs.unstandardized)
```

Forest Plot for Incremental Costs
```{r}
forest.costs<-subset(Incremental_costs, select = c(Study_ID,Intervention_Type,Incremental_Costs,Incremental_Costs_LL95CI, 
                                                   Incremental_Costs_UL95CI))
forest.costs$Effect_size<-c(2:24)
forest.costs$Study_InterventionType<-paste(forest.costs$Study_ID,forest.costs$Intervention_Type)
forest.costs$rev_ES<-rev(forest.costs$Effect_size)  
Overall.effect<-c("Overall", NA, 356, -178, 890, 1, "Overall", 1)
forest.costs.plot<-rbind(forest.costs, Overall.effect)
forest.costs.plot$rev_ES<-as.numeric(forest.costs.plot$rev_ES)
forest.costs.plot$Incremental_Costs<-as.numeric(forest.costs.plot$Incremental_Costs)
forest.costs.plot$Incremental_Costs_LL95CI<-as.numeric(forest.costs.plot$Incremental_Costs_LL95CI)
forest.costs.plot$Incremental_Costs_UL95CI<-as.numeric(forest.costs.plot$Incremental_Costs_UL95CI)

Incremental.Costs.plot<-ggplot(forest.costs.plot, aes(y=rev_ES, x=Incremental_Costs, xmin=Incremental_Costs_LL95CI, xmax=Incremental_Costs_UL95CI)) +
  geom_point() + geom_errorbarh(height=.1) + scale_y_continuous(name= "", breaks=rev(1:nrow(forest.costs.plot)), labels=forest.costs.plot$Study_InterventionType) +
  labs(title="Incremental Costs Forest Plot", x="Incremental Costs (2021 USD)", y = "Author, Year, Intervention Type" ) + 
  geom_vline(xintercept=0, color="black", linetype="dashed", alpha=.5) + theme_classic()

Incremental.Costs.plot
```

Incremental QALYs (Unstandardized estimates)
```{r}
incremental_qolys.unstandardized<-robu(Incremental_QoLYs~1, var=Incremental_QOLYs_Variance, studynum=Study_ID, Incremental_QOLYs)
print(incremental_qolys.unstandardized)
sensitivity(incremental_qolys.unstandardized)
```

Forest Plot for Incremental QALYs
```{r}
forest.qolys<-subset(Incremental_QOLYs, select = c(Study_ID,Intervention_Type,Incremental_QoLYs,Incremental_QOLYs_LL95CI, 
                                                   Incremental_QOLYs_UL95CI))
forest.qolys$Effect_size<-c(2:16)
forest.qolys$Study_InterventionType<-paste(forest.qolys$Study_ID,forest.qolys$Intervention_Type)
forest.qolys$rev_ES<-rev(forest.qolys$Effect_size)  
Overall.effect<-c("Overall", NA, 0.0878, -0.308, 0.483, 1, "Overall", 1)
forest.qolys.plot<-rbind(forest.qolys, Overall.effect)
forest.qolys.plot$rev_ES<-as.numeric(forest.qolys.plot$rev_ES)
forest.qolys.plot$Incremental_QoLYs<-as.numeric(forest.qolys.plot$Incremental_QoLYs)
forest.qolys.plot$Incremental_QOLYs_LL95CI<-as.numeric(forest.qolys.plot$Incremental_QOLYs_LL95CI)
forest.qolys.plot$Incremental_QOLYs_UL95CI<-as.numeric(forest.qolys.plot$Incremental_QOLYs_UL95CI)

Incremental.Qolys.plot<-ggplot(forest.qolys.plot, aes(y=rev_ES, x=Incremental_QoLYs, xmin=Incremental_QOLYs_LL95CI, xmax=Incremental_QOLYs_UL95CI)) +
  geom_point() + geom_errorbarh(height=.1) + scale_y_continuous(name= "", breaks=rev(1:nrow(forest.qolys.plot)), labels=forest.qolys.plot$Study_InterventionType) +
  labs(title="Incremental QOLYs Forest Plot", x="Incremental QOLYs", y = "Author, Year, Intervention Type" ) + 
  geom_vline(xintercept=0, color="black", linetype="dashed", alpha=.5) + theme_classic()

Incremental.Qolys.plot
```

Incident Rate for Falls using Hedge's g. Estimates are re-transformed by exponentiation
```{r}
falls.g<-robu(IRR_of_Falls_g~1, var=IRR_of_Falls_g_var, studynum=Study_ID, IRR_Falls)
print(falls.g)
sensitivity(falls.g)
irr.exp<-c(falls.g$reg_table$b.r, falls.g$reg_table$CI.L, falls.g$reg_table$CI.U)
exp(irr.exp) #Point Estimate, 95% CI LL, 95% CI UL
```

Forest Plot for Incident Rate of Falls. Estimates are re-transformed by exponentiation
```{r}
forest.IRRs<-subset(IRR_Falls, select = c(Study_ID,Intervention_Type,IRR_of_Falls_g,IRR_Falls_SMD_LL95CI, 
                                          IRR_Falls_SMD_UL95CI))
forest.IRRs$Effect_size<-c(2:16)
forest.IRRs$Study_InterventionType<-paste(forest.IRRs$Study_ID,forest.IRRs$Intervention_Type)
forest.IRRs$rev_ES<-rev(forest.IRRs$Effect_size)  
Overall.effect<-c("Overall", NA, -0.665, -1.04, -0.294, 1, "Overall", 1)
forest.IRRs.plot<-rbind(forest.IRRs, Overall.effect)
forest.IRRs.plot$rev_ES<-as.numeric(forest.IRRs.plot$rev_ES)
forest.IRRs.plot$IRR_of_Falls_g<-as.numeric(forest.IRRs.plot$IRR_of_Falls_g)
forest.IRRs.plot$IRR_Falls_SMD_LL95CI<-as.numeric(forest.IRRs.plot$IRR_Falls_SMD_LL95CI)
forest.IRRs.plot$IRR_Falls_SMD_UL95CI<-as.numeric(forest.IRRs.plot$IRR_Falls_SMD_UL95CI)
forest.IRRs.plot$IRR_exp<-exp(forest.IRRs.plot$IRR_of_Falls_g)
forest.IRRs.plot$UL_exp<-exp(forest.IRRs.plot$IRR_Falls_SMD_UL95CI)
forest.IRRs.plot$LL_exp<-exp(forest.IRRs.plot$IRR_Falls_SMD_LL95CI)

IRR.plot<-ggplot(forest.IRRs.plot, aes(y=rev_ES, x=IRR_exp, xmin=LL_exp, xmax=UL_exp)) +
  geom_point() + geom_errorbarh(height=.1) + scale_y_continuous(name= "", breaks=rev(1:nrow(forest.IRRs.plot)), labels=forest.IRRs.plot$Study_InterventionType) +
  labs(title="Incident Rate Ratio of Falls Forest Plot", x="Incident Rate Ratio", y = "Author, Year, Intervention Type" ) + 
  geom_vline(xintercept=1, color="black", linetype="dashed", alpha=.5) + theme_classic()

IRR.plot
```

# 4) Does Intervention Type (EX vs. EX-Plus) moderate the effects on incremental costs, QALYs, or incident rate of falls

Incremental Costs
```{r}
robu(Incremental_Costs~Intervention_Type-1, var.eff.size = Incremental_Costs_Variance, studynum = Study_ID, data = Incremental_costs)
costs.mod<-robu(Incremental_Costs~Intervention_Type-1, var.eff.size = Incremental_Costs_Variance, studynum = Study_ID, data = Incremental_costs)
cpairs<- constraints<-matrix(c(1,-1), 1,2)
Wald_test(costs.mod, constraints = cpairs, vcov = "CR2", tidy = TRUE)
```

Incremental QALYs
```{r}
robu(Incremental_QoLYs~Intervention_Type-1, var.eff.size = Incremental_QOLYs_Variance, studynum = Study_ID, data = Incremental_QOLYs)
qolys.mod<-robu(Incremental_QoLYs~Intervention_Type-1, var.eff.size = Incremental_QOLYs_Variance, studynum = Study_ID, data = Incremental_QOLYs)
cpairs<- constraints<-matrix(c(1,-1), 1,2)
Wald_test(qolys.mod, constraints = cpairs, vcov = "CR2", tidy = TRUE)
```

Incident Rate of Falls
```{r}
falls.mod<-robu(IRR_of_Falls_SMD~Intervention_Type-1, var.eff.size = IRR_of_Falls_SMD_var, studynum = Study_ID, data = IRR_Falls)
falls.mod
cpairs<- constraints<-matrix(c(1,-1), 1,2)
Wald_test(falls.mod, constraints = cpairs, vcov = "CR2", tidy = TRUE)

irr.exp<-c(falls.mod$reg_table$b.r, falls.mod$reg_table$CI.L, falls.mod$reg_table$CI.U)
irr.exp
exp(irr.exp) #Point Estimate EX, Point Estimate EX-Plus, 95% CI LL EX, 95% CI LL EX-Plus, 95% CI UL EX, 95% CI UL EX-Plus

```

# 5) Funnel Plots for Publication Bias

Incremental Costs
```{r}
meta.res.costs<-rma.mv(yi=Incremental_Costs_g,V=Incremental_Costs_g_var,data=Incremental_costs,slab=Study_ID)
funnel(meta.res.costs, xlab = "Hedge's g for incremental costs")
```

Incremental QALYs
```{r}
meta.res.qolys<-rma.mv(yi=Incremental_QOLYs_g,V=Incremental_QOLYs_g_var,data=Incremental_QOLYs,slab=Study_ID)
funnel(meta.res.qolys, xlab = "Hedge's g for incremental QALYs")
```

Incident Rate of Falls
```{r}
meta.res.falls<-rma.mv(yi=IRR_of_Falls_g,V=IRR_of_Falls_g_var,data=IRR_Falls,slab=Study_ID)
funnel(meta.res.falls, xlab = "Hedge's g for IRR of Falls")
```

# 6) PEESE

Incremental Costs
```{r}
Incremental_costs$sesqrd.ES<-Incremental_costs$Incremental_Costs_g_se^2
peese.rve.costs <- robu(Incremental_Costs_g~sesqrd.ES, var.eff.size = Incremental_Costs_g_var, studynum = Study_ID, data = Incremental_costs)
print(peese.rve.costs)
```

Incremental QALYs
```{r}
Incremental_QOLYs$sesqrd.ES<-Incremental_QOLYs$Incremental_QOLYs_g_se^2
peese.rve.qoly <- robu(Incremental_QOLYs_g~sesqrd.ES, var.eff.size = Incremental_QOLYs_g_var, studynum = Study_ID, data = Incremental_QOLYs)
print(peese.rve.qoly)
```

Incident Rate of Falls
```{r}
IRR_Falls$sesqrd.ES<-IRR_Falls$IRR_of_Falls_g_se^2
peese.rve.falls <- robu(IRR_of_Falls_g~sesqrd.ES, var.eff.size = IRR_of_Falls_g_var, studynum = Study_ID, data = IRR_Falls)
print(peese.rve.falls)
```

# 7) Egger's Regression Test for Dependent Effect Sizes

Incremental Costs
```{r}
pet.rve.cost<-robu(Incremental_Costs_g~Incremental_Costs_g_se, var.eff.size=Incremental_Costs_g_var, 
                   studynum=Study_ID, data=Incremental_costs)

print(pet.rve.cost)
```

Incremental QALYs
```{r}
pet.rve.qolys<-robu(Incremental_QOLYs_g~Incremental_QOLYs_g_se, var.eff.size=Incremental_QOLYs_g_var, 
                   studynum=Study_ID, data=Incremental_QOLYs)

print(pet.rve.qolys)
```

Incident Rate of Falls
```{r}
pet.rve.falls<-robu(IRR_of_Falls_g~IRR_of_Falls_g_se, var.eff.size=IRR_of_Falls_g_var, 
                    studynum=Study_ID, data=IRR_Falls)

print(pet.rve.falls)
```

# 8) Leave-One-Out Analyses

Incremental Costs
```{r}
leave.one.out.all<- function(rownum){
  
  # subset dataframe
  vec <- rep(TRUE, nrow(Incremental_costs))
  vec[rownum] <- FALSE
  inf <- subset(Incremental_costs, vec)
  
  # fit reference model
  rve.model.ref <- robu(Incremental_Costs~1,var=Incremental_Costs_Variance,studynum=Study_ID, Incremental_costs)
  
  # fit adjusted model
  rve.model <- robu(Incremental_Costs~1,var=Incremental_Costs_Variance,studynum=Study_ID, data = inf)
  
  # return results
  results.vec <- c(ES.study = round(Incremental_costs$Incremental_Costs[rownum], 3),
                   ES.adj = round(rve.model$reg_table$b.r, 3),
                   se.ES.adj = round(rve.model$reg_table$SE, 3),
                   p.adj = round(rve.model$reg_table$prob, 5),
                   diff.ES = round(rve.model$reg_table$b.r - rve.model.ref$reg_table$b.r, 3),
                   diff.se.ES = round(rve.model$reg_table$SE - rve.model.ref$reg_table$SE, 3),
                   diff.p = round(rve.model$reg_table$prob - rve.model.ref$reg_table$prob, 5),
                   diff.isq = round(rve.model$mod_info$I.2 - rve.model.ref$mod_info$I.2, 3))
  return(results.vec)
}

inf.all <- sapply(1:nrow(Incremental_costs), leave.one.out.all)
inf.all <- data.frame(t(inf.all))
inf.all <- data.frame(label = paste(Incremental_costs$Study_ID, Incremental_costs$Intervention_Type, sep = " / "),
                      inf.all)
inf.all$z.ES.study <- round(scale(inf.all$ES.study), 2)

inf.all
```

Incremental QALYs
```{r}
leave.one.out.all.qoly<- function(rownum){
  
  # subset dataframe
  vec <- rep(TRUE, nrow(Incremental_QOLYs))
  vec[rownum] <- FALSE
  inf <- subset(Incremental_QOLYs, vec)
  
  # fit reference model
  rve.model.ref <- robu(Incremental_QoLYs~1,var=Incremental_QOLYs_Variance,studynum=Study_ID, Incremental_QOLYs)
  
  # fit adjusted model
  rve.model <- robu(Incremental_QoLYs~1,var=Incremental_QOLYs_Variance,studynum=Study_ID, data = inf)
  
  # return results
  results.vec <- c(ES.study = round(Incremental_QOLYs$Incremental_QoLYs[rownum], 3),
                   ES.adj = round(rve.model$reg_table$b.r, 3),
                   se.ES.adj = round(rve.model$reg_table$SE, 3),
                   p.adj = round(rve.model$reg_table$prob, 5),
                   diff.ES = round(rve.model$reg_table$b.r - rve.model.ref$reg_table$b.r, 3),
                   diff.se.ES = round(rve.model$reg_table$SE - rve.model.ref$reg_table$SE, 3),
                   diff.p = round(rve.model$reg_table$prob - rve.model.ref$reg_table$prob, 5),
                   diff.isq = round(rve.model$mod_info$I.2 - rve.model.ref$mod_info$I.2, 3))
  return(results.vec)
}

inf.all <- sapply(1:nrow(Incremental_QOLYs), leave.one.out.all.qoly)
inf.all <- data.frame(t(inf.all))
inf.all <- data.frame(label = paste(Incremental_QOLYs$Study_ID, Incremental_QOLYs$Intervention_Type, sep = " / "),
                      inf.all)
inf.all$z.ES.study <- round(scale(inf.all$ES.study), 2)

inf.all
```

Incident Rate of Falls
```{r}
leave.one.out.all.falls<- function(rownum){
  
  # subset dataframe
  vec <- rep(TRUE, nrow(IRR_Falls))
  vec[rownum] <- FALSE
  inf <- subset(IRR_Falls, vec)
  
  # fit reference model
  rve.model.ref <- robu(IRR_of_Falls_g~1,var=IRR_of_Falls_g_var,studynum=Study_ID, IRR_Falls)
  
  # fit adjusted model
  rve.model <- robu(IRR_of_Falls_g~1,var=IRR_of_Falls_g_var,studynum=Study_ID, data = inf)
  
  # return results
  results.vec <- c(ES.study = round(IRR_Falls$IRR_of_Falls_g[rownum], 3),
                   ES.adj = round(rve.model$reg_table$b.r, 3),
                   se.ES.adj = round(rve.model$reg_table$SE, 3),
                   p.adj = round(rve.model$reg_table$prob, 5),
                   diff.ES = round(rve.model$reg_table$b.r - rve.model.ref$reg_table$b.r, 3),
                   diff.se.ES = round(rve.model$reg_table$SE - rve.model.ref$reg_table$SE, 3),
                   diff.p = round(rve.model$reg_table$prob - rve.model.ref$reg_table$prob, 5),
                   diff.isq = round(rve.model$mod_info$I.2 - rve.model.ref$mod_info$I.2, 3))
  return(results.vec)
}

inf.all <- sapply(1:nrow(IRR_Falls), leave.one.out.all.falls)
inf.all <- data.frame(t(inf.all))
inf.all <- data.frame(label = paste(IRR_Falls$Study_ID, IRR_Falls$Intervention_Type, sep = " / "),
                      inf.all)
inf.all$z.ES.study <- round(scale(inf.all$ES.study), 2)

inf.all
```


# 9) Do the effects differ if Farag et al. and Patil et al. are excluded from the meta?

Both studies had incremental costs estimated using ICER data.

Mark studies with estimated (i.e., Farag et al. and Patil et al.) versus reported incremental costs
```{r}
Incremental_costs$ES_calculation<-NA
Incremental_costs$ES_calculation[Incremental_costs$Study_ID=="Farag et al., 2015" |
                                   Incremental_costs$Study_ID=="Patil et al., 2015" ]<-"Estimated"
Incremental_costs$ES_calculation[Incremental_costs$Study_ID!="Farag et al., 2015" &
                                   Incremental_costs$Study_ID!="Patil et al., 2015" ]<-"Reported"
```

Moderation effect for determining if effect is different when excluding studies with estimated incremental costs
```{r}
robu(Incremental_Costs~ES_calculation-1, var.eff.size = Incremental_Costs_Variance, studynum = Study_ID, data = Incremental_costs)
```